\LARGE HIV virulence evolution in structured epidemic models

### 2016-05-30 poster/hivlhs_eeid2016.Rnw
working on poster

%\documentclass[final,hyperref={pdfpagelabels=false}]{beamer}
\documentclass{beamer}
\usepackage{grffile}
\mode<presentation>{\usetheme{mcmaster}}

@@

@@

<<setup3,echo=FALSE>>=
source("../R/hivFuns.R")
source("../R/Param.R")
ltab_mean <- apply(HIVpars_range, 1, geom_mean)
HIVpars.base <- as.HIVvirparlist(ltab_mean)
Lspvl <- "$\\log_{10}~\\textrm{SPVL}$"
pars <- expand(HIVpars.base)
dd <-with(pars,
     melt(data.frame(alpha=alpha,"transmission probability"=Beta2,
                     "duration (years)"=Duration2,check.names=FALSE),
          id.vars="alpha"))
gg_tradeoff <- ggplot(dd,aes(alpha,value))+facet_wrap(~variable,scale="free")+
    geom_line()+
    labs(x= Lspvl)
@

@@

<<tradeoff_fig,echo=FALSE,fig.height=14,fig.width=30,out.width="0.95\\textwidth",dev="tikz",cache=TRUE>>=
print(gg_tradeoff)
@

\begin{itemize}
\item \textbf{tradeoff theory}: virulence evolution mediated by transmission-vs-clearance tradeoff
\item still debated \cite{EbertBull2003,alizon_adaptive_2015}
\item HIV \cite{fraser_virulence_2014}: \textbf{set-point viral load}
      correlated with transmission probability, rate of progression to AIDS (data from Rakai, Uganda)
\item eco-evolutionary virulence dynamics: \cite{shirreff_transmission_2011}
\end{itemize}

@@

\begin{block}{Basic eco-evolutionary dynamics}

@@

<<univ,cache=TRUE,dev="tikz",fig.width=45,fig.height=40,out.width="0.95\\textwidth">>=
sL <- transform(sum_list[["sum_mat"]],rel_peak=peak_vir/eq_vir)
sL$model <- factor(sL$model, c("random","pairform+epc", "pairform", "instswitch+epc","instswitch" , "implicit"))
mL <- melt(sL,id.vars=c("model","run"))
## horrible hack (but doesn't help); subsample
## w <- which(mL$model=="random")
## mLw <- mL[-sample(w,size=length(w)*9/10,replace=FALSE),]
w <- with(mL,which(model=="random" & variable=="eq_vir"))
rval <- mean(mL$value[w])
mLw <- droplevels(mL[-w,])
mLw$variable <- fixfac2(mLw$variable)

gg_univ <- ggplot(mLw,aes(value,model,fill=model))+
    geom_violinh(width=1)+
    facet_wrap(~variable,scale="free_x")+
    guides(fill=guide_legend(reverse=TRUE))+
    labs(y="")+
    geom_point(data=data.frame(model="random",
                               variable="equilibrium virulence",
                               value=rval),
               pch=22,size=8,show.legend=FALSE) +
    theme(legend.position="none")+
    zero_x_margin
print(gg_univ)
@

>>>>

%\documentclass[final,hyperref={pdfpagelabels=false}]{beamer}
\documentclass{beamer}
\usepackage{ebgaramond}
%% reset default
\renewcommand{\rmdefault}{cmss}
\usepackage{grffile}
\mode<presentation>{\usetheme{mcmaster}}

@@

% http://tex.stackexchange.com/questions/13423/how-to-change-the-color-of-href-links-for-real
\hypersetup{colorlinks,linkcolor=}

@@

<<setup3,echo=FALSE,cache=TRUE>>=
source("../R/hivFuns.R")
source("../R/Param.R")
ltab_mean <- apply(HIVpars_range, 1, geom_mean)
HIVpars.base <- as.HIVvirparlist(ltab_mean)
Lspvl <- "$\\log_{10}~\\textrm{SPVL}$"
pars <- expand(HIVpars.base)
dd <-with(pars,
     melt(data.frame(alpha=alpha,"transmission probability"=Beta2,
                     "duration (years)"=Duration2,check.names=FALSE),
          id.vars="alpha"))
gg_tradeoff <- ggplot(dd,aes(alpha,value))+facet_wrap(~variable,scale="free")+
    geom_line(size=10)+
    labs(x= Lspvl,y="")
@

@@

<<tradeoff_fig,echo=FALSE,fig.height=14,fig.width=30,out.width="0.95\\textwidth",dev="tikz",cache=TRUE,dependson="setup3">>=
print(gg_tradeoff)
@

\begin{itemize}
\item virulence evolution mediated by transmission-vs-clearance tradeoff
\item still debated \cite{EbertBull2003,alizon_adaptive_2015}
\item HIV \cite{fraser_virulence_2014}: \textbf{set-point viral load}
      correlated with transmission probability, rate of progression to AIDS (data from Rakai, Uganda)
\item eco-evolutionary virulence dynamics: \cite{shirreff_transmission_2011}
\end{itemize}

@@

\begin{block}{Eco-evolutionary dynamics}

@@

<<univ,cache=TRUE,dev="tikz",fig.width=30,fig.height=30,out.width="0.95\\textwidth">>=
sL <- transform(sum_list[["sum_mat"]],rel_peak=peak_vir/eq_vir)
sL$model <- factor(sL$model, c("random","pairform+epc", "pairform", "instswitch+epc","instswitch" , "implicit"))
mL <- melt(sL,id.vars=c("model","run"))
## horrible hack (but doesn't help); subsample
## w <- which(mL$model=="random")
## mLw <- mL[-sample(w,size=length(w)*9/10,replace=FALSE),]
w <- with(mL,which(model=="random" & variable=="eq_vir"))
rval <- mean(mL$value[w])
mLw <- droplevels(mL[-w,])
mLw$variable <- fixfac2(mLw$variable)

gg_univ <- ggplot(mLw,aes(value,model,fill=model))+
    geom_violinh(width=1)+
    facet_wrap(~variable,scale="free_x")+
    guides(fill=guide_legend(reverse=TRUE))+
    labs(y="",x="")+
    geom_point(data=data.frame(model="random",
                               variable="equilibrium virulence",
                               value=rval),
               pch=22,size=8,show.legend=FALSE) +
    theme(legend.position="none")+
    zero_x_margin
print(gg_univ)
@
